Timely Object Recognition

### 2012-05-30 writeups/nips12/evaluation.tex
fixing gist oracle

\begin{figure}[h!]
\centering
\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
    {../figures/entropy_plots_det_avg.png}} \\
\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
    {../figures/entropy_plots_cls_whole.png}}
  \caption{Entropy reward function.}
  \label{fig:results_entropy}
\end{figure}

Figure~\ref{fig:results_entropy} shows the performance of the polices with learned weights, comparing our two reward functions.
We found the entropy-based reward to work better than the AP-based reward.

A notable difference between the MRF inference model and the fixed-order model was in the weights learned: while the fixed-order model learned weights onto the bias feature only, the MRF inference model learned weights onto a mix of the entropy and probability features.

>>>>

A notable difference between the MRF inference model and the fixed-order model was in the weights learned: while the fixed-order model learned weights onto the bias feature only, the MRF inference model learned weights onto a mix of the entropy and probability features
